Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-27 docs/msr.tex
minor chnges

{\it Refactoring identification} through software evolution is an approach used to
relate refactorings with software bugs. Weibgerber et al. found that a high
ratio of refactorings is usually followed by an increasing ratio of bug
reports~\cite{WD06}. In addition, they found that software bugs are sometimes introduced
after an incomplete refactoring~\cite{GW05}.
Ratzinger et al.~\cite{RSG08} found that the number of bugs decreases, when the number of
refactorings increases. Finally, Kim M. et al.~\cite{KCK11} showed that {\sc api}-level
refactorings aid bug fixes.

Using {\it micro patterns} is an approach proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern.

>>>>

{\it Refactoring identification} through software evolution is an approach used to
relate refactorings with software bugs. Wei{\ss}gerber et al. found that a high
ratio of refactorings is usually followed by an increasing ratio of bug
reports~\cite{WD06}. In addition, they indicated that software bugs are sometimes introduced
after an incomplete refactoring~\cite{GW05}.
Ratzinger et al.~\cite{RSG08} found that the number of bugs decreases, when the number of
refactorings increases. Finally, Kim M. et al.~\cite{KCK11} showed that {\sc api}-level
refactorings aid bug fixes.

Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern.
